## Notes

For each species, manual curation is necessary to produce a usable sample sheet (in most cases). These are processing notes on each species.

### Setup

First we load libraries

```{r}
library(tidyverse)
library(stringr)
library(tabulizer)
library(readxl)
```

Then we set some default processing. For all datasets, we need the BioProject (to link to publication), the BioSample (to link to VCF), and Organism. 

```{r}
clean_metadata_path <- "~/Projects/popgen/compPopGen_ms/SRA/cleaned-metadata/"
raw_metadata_path <- "~/Projects/popgen/compPopGen_ms/SRA/SRA-sample-metadata/"

get_sra <- function(sp, path=raw_metadata_path, opt_cols) {
  default_cols = c("BioProject", "BioSample", "Organism", "sex")
  if (missing(opt_cols)) {
    cols = enquo(default_cols)
  } else {
    default_cols = c(default_cols, opt_cols)
    cols = enquo(default_cols)
  }
  read_tsv(str_c(raw_metadata_path, "SRA_Metadata_", sp, ".tsv")) %>% 
    select(!!cols)
}
  
```

## METADATA CODE BELOW ##

### Amphilophus citrinellus

Sample metadata downloaded from: https://datadryad.org/stash/dataset/doi:10.5061/dryad.bcc2fqz91

Keyed on sample it / submitter id.


```{r}
sp="Amphilophus_citrinellus"
sra<-get_sra(sp, opt_cols = c("Submitter_Id")) %>%
  mutate(Submitter_Id = str_remove(Submitter_Id, "_WGS"))
dryad_link<-"https://datadryad.org/stash/downloads/file_stream/561311"
paper<-read_csv(dryad_link) %>% select(Sample_name, Species, Lake, Sampling_Year)
inner_join(paper,sra,by=c("Sample_name" = "Submitter_Id")) %>% write_csv(str_c(clean_metadata_path, sp, "_meta.csv"))
```

### Anas platyrhynchos

Sample metadata embedded in PDF in supplemental material: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6050300/bin/41467_2018_4868_MOESM1_ESM.pdf

```{r}
sp="Anas_platyrhynchos"
sra<-get_sra(sp, opt_cols = c("Sample_Type", "sex")) %>% 
  mutate(Sample_Type = str_remove(Sample_Type, "_F"))

supmat<-"https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6050300/bin/41467_2018_4868_MOESM1_ESM.pdf"
paper<-do.call(rbind,extract_tables(supmat, pages=c(38:40)))
colnames(paper) <- c("sample", "breed", "mapping_rate", "insert_size", "depth")

paper %>% as_tibble %>% select(sample, breed) %>% 
  filter(breed != "Breed", breed != "") %>% 
  left_join(sra, by=c("sample" = "Sample_Type")) %>%
  write_csv(str_c(clean_metadata_path, sp, "_meta.csv"))
```

### Anguilla anguilla

Metadata provided to SRA is great and totally complete, no need to dig into paper.
Generally this is very low coverage data, with only a fraction of individuals above 5x, so may not be great.
Closely related species Anguilla rostrata also available

```{r}
sp="Anguilla_anguilla"

sra<-get_sra(sp, opt_cols = c("Isolate", "Ecotype", "Collection_date", "lat_lon", 
                              "geo_loc_name_country", "geo_loc_name_country_continent", 
                              "geo_loc_name")) %>%
  rename(Country=geo_loc_name_country, 
         Continent=geo_loc_name_country_continent,
         Locality=geo_loc_name) %>% 
    write_csv(str_c(clean_metadata_path, sp, "_meta.csv"))
```

### Anolis carolinensis

Single individuals of A. porcatus and A. allisoni in same BioProject.

Metadata is okay, but need to get more info about location from the paper: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6681179/

Locked in a Zip archive so need to process

```{r}
sp="Anolis_carolinensis"

sra<-get_sra(sp, opt_cols = c("Sample Name", "Sample_Type")) %>% 
  rename(Submitter_Id = `Sample Name`, Isolate = Sample_Type)

supmat<-"https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6681179/bin/evz110_supplementary_data.zip"
temp <- tempfile()
download.file(supmat,temp)
unzip(temp, files=c("Table_S1.xlsx"), junkpaths=TRUE, exdir=raw_metadata_path)
paper<-read_excel(str_c(raw_metadata_path, "Table_S1.xlsx")) %>% select(Sample:Longitude)
unlink(temp)

inner_join(paper, sra, by=c("Sample" = "Submitter_Id")) %>% 
  write_csv(str_c(clean_metadata_path, sp, "_meta.csv"))
```

### Astatotilapia calliptera

This dataset is complex, spanning many species in the cichild flock. Best to process by BioProject, not species. The metadata is also terrible and poorly organized / hard to parse.

Will need to think a bit about whether this is usable, but the metadata is here if needed.

```{r}
sp="Astatotilapia_calliptera"
bp="PRJEB1254"

sra<-get_sra(bp, opt_cols = c("Organism", "Alias")) %>% 
  rename(Submitter_Id = Alias)

supmat1<-"https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4700518/bin/NIHMS66047-supplement-01.pdf"
table16<-do.call(rbind,extract_tables(supmat, pages=c(47:47)))
colnames(table16) <- c("SampleName", "BioSample")

paper1<-as_tibble(table16) %>% separate_rows(BioSample, sep=",") %>% filter(SampleName != "Samples") %>%
  filter(BioSample != "") %>%
  separate_rows(BioSample, sep=",") %>%
  mutate(BioSample = str_remove(BioSample, "\\r")) %>%
  mutate(BioSample = trimws(BioSample)) %>%
  mutate(BioSample = split_biosample(BioSample)) %>%
  separate_rows(BioSample) %>% select(BioSample, SampleName) %>%
  mutate(BioSample = str_c("SAMEA", BioSample))

supmat2<-"https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6443041/bin/NIHMS82209-supplement-Supplementary_information.pdf"
table4 <- do.call(rbind,extract_tables(supmat2, pages=c(50:50)))
colnames(table4) <- c("SampleName", "BioSample")

paper2<-as_tibble(table4) %>% filter(SampleName != "Samples") %>%
  mutate(SampleNameClean = c(rep("Lake Malawi populations",11), rep("Lake Malawi trios",3), 
                        rep("Malawi catchment", 2), rep("Indian ocean catchments", 2),
                        rep("Outgroup", 6))) %>%
  filter(BioSample != "") %>%
  separate_rows(BioSample, sep=",") %>%
  mutate(BioSample = str_remove(BioSample, "A. stuartgranti")) %>%
  mutate(BioSample = str_remove(BioSample, "L. lethrinus")) %>%
  mutate(BioSample = str_remove(BioSample, "A. calliptera Salima")) %>%
  mutate(BioSample = trimws(BioSample)) %>%
  filter(str_detect(BioSample, "SAMEA")) %>%
  mutate(BioSample = str_replace(BioSample, "SAMEA1904329-", "SAMEA1904329-SAMEA1904331")) %>%
  mutate(BioSample = str_replace(BioSample, "SAMEA1904350-", "SAMEA1904350-SAMEA1904353")) %>%
  mutate(BioSample = trimws(BioSample)) %>%
  mutate(BioSample = split_biosample(BioSample)) %>%
  separate_rows(BioSample) %>% select(BioSample, SampleNameClean) %>%
  mutate(BioSample = str_c("SAMEA", BioSample))

full_join(paper1, paper2, by=c("BioSample" = "BioSample")) %>% distinct() %>% 
  full_join(sra, by=c("BioSample" = "BioSample")) %>% distinct() %>%
  rename(SampleName1 = SampleName, SampleName2 = SampleNameClean) %>%
  filter(!is.na(BioProject)) %>%
  write_csv(str_c(clean_metadata_path, bp, "_meta.csv"))
```


### Astyanax mexicanus

Beautiful metadata, everything in SRA submission

```{r}
sp="Astyanax_mexicanus"
  
sra<-get_sra(sp, opt_cols = c("Sample Name")) %>% 
  rename(Submitter_Id = `Sample Name`) %>%
  separate(Submitter_Id, into=c("Population"), remove=FALSE, extra="drop")

sra %>% write_csv(str_c(clean_metadata_path, bp, "_meta.csv"))

```

